Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-05-29 raspi_journal.tex
Include buildbot and documentation descriptions and cite

\item Navigate to the repository and configure \texttt{waf} by typing:
\texttt{python config.py} and select the 16th ``make specification'' file
for the Raspberry Pi which is option \texttt{[16]cxx\_raspberry\_gxx49\_arm}
presented by the file.

@@

\subsection{Kodo Builds, Platform Support and Documentation}
Link to the buildbot and the relevant webpages providing a description
of them.

>>>>

\item Navigate to the repository and configure \texttt{waf} by typing:
\texttt{python config.py} and select the 16th ``make specification'' file
for the Raspberry Pi, e.g. option \texttt{[16]cxx\_raspberry\_gxx49\_arm}
presented by the file.

@@

\subsection{Kodo Builds for the Raspberry Pi, Platform Support and Documentation}

You can check the build status of Kodo, Fifi and other relevant projects through
their respective repository master branch on our buildbot page
\cite{steinwurf2016buildbot}. Our buildbot displays the status of the builds for
Raspbian 8 and GCC 4.9 for the ARM architecture which is the relevant one for the
Raspberry Pi. At the link, you can check build status and build statistics. Also,
documentation about Kodo basics with a tutorial is available at \cite{kododocs}.
